We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-06 paper/paper.tex
edit

In both cases the strongest positive correlation is present for the

\subsection{Number of Expected LG Systems}
This is all the information that is needed to compute the fraction of
pairs that are expected to share the same asphericity as the LG.
We start the Discussion section by describing the results of
performing such a computation.

>>>>

In both cases the strongest positive correlation is present for the
width and the $c/a$ axis ratio. A weaker but still positive
correlation is present for the width and the $b/a$ axis ratio.

\subsection{Number of Expected LG Systems}

The fits to the multivariate gaussian distributions can be used now to
compute the expected number of pairs with characteristics similar to
the LG.
To do this we generate $10^3$ samples, each sample contains $10^4$
pairs which are drawn from the multivariate gaussian distributions.

Figure \ref{fig:expected_number} summarizes the results from this
experiment. 
The left panel
